Workflow

### 2014-12-01 Workflow/Workflow.Rmd
DownloadPostProcessed.R now exists. It accepts a comma-separated list of <Source>s.

### Download post-processed results to local machine
* From a local machine, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source> -d`, where `<user>` is 
a username on `dahl`, `<Source>` is the data source of interest, and `-d` (debug) will 
show the files to be transferred to the local machine, without actually transferring them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source>` to download the files.
* The files are downloaded to the `data_postprocessed` directory on the local machine.
* Use the function `loadPostProcessedData` in the `EconData` package to load the downloaded data into
the environment. 
* The `DownloadPostProcessed.bash` script connects to `dahl.calvin.edu` (`node-00`). 
That choice was made to minimize the risk that a file won't prpogate across the cluster 
file system prior to the download request.

>>>>

### Download post-processed results to local machine
* From the `Econ-Growth-R-Analysis` directory of a local machine, 
say `Scripts/DownloadPostProcessed.R -u <user> -S <Source> -d`, where `<user>` is 
a username on `dahl`, `<Source>` is a comma-separated list of data sources of interest, and `-d` (debug) will 
show the files to be transferred to the local machine, without actually transferring them.
* Verify that the list of files to be transferred looks right.
* From a local computer, say `Scripts/DownloadPostProcessed.R -u <user> -S <Source>` to download the files.
* The files are downloaded to the `data_postprocessed` directory on the local machine.
* Use the function `loadPostProcessedData` in the `EconData` package to load the downloaded data into
the environment. 
* The `DownloadPostProcessed.R` script connects to `dahl.calvin.edu` (`node-00`). 
The choice to connect to `node-00` was made to minimize the risk that a file won't propagate across the cluster's 
file system prior to the download request.
